Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-03 paper/paper.tex
Moved comment outside subfloat

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.\Gustavo{Não esquecer de atualizar as figuras.
  }]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

>>>>

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
  }}
  \vspace{-3ex}
\end{figure}
